---
title: "simpleRegress"
author: "Tracy Alset"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

Using the neck variable is better than the weight because the adjusted r squared for neck is higher than weight(the closer it is to 1 the better the variable is) and the residual standard error for weight is higher than neck.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```


The adjusted  R-squared value for age is lower than both neck and weight, and the residual standard error is between the last two variables, so the age variable isn't better than neck.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

the adjusted R-squared value for head width is lower than neck and the residual standard errorfor head width is higher than , so it's not a better variable than neck.


```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

the head length variable is the best one so far because it has the highest adjusted R- squared value ( even higher than the neck variable) an it has the lowest residual standard error.


### conclusion:
In this type of project, we compared the relation between one specific variable and another variable by comparing the adjusted R-squared value and the residual standard error. ( the higher the r- squared value and the lower the residual standard error the better the variable chosen is).


